Main manuscript

### 2021-10-26 Manuscript/Manuscript.Rmd
fixed locazation problem that was misplacing commas around quot marks

---
title: Main manuscript
authors:
  - name: David S. Hippocampus
    thanks: Use footnote for providing further information about author (webpage, alternative address)---*not* for acknowledging funding agencies. Optional.
    department: Department of Computer Science
    affiliation: Cranberry-Lemon University
    location: Pittsburgh, PA 15213
    email: hippo@cs.cranberry-lemon.edu
  - name: Elias D. Striatum
    department: Department of Electrical Engineering
    affiliation: Mount-Sheikh University
    location: Santa Narimana, Levand
    email: stariate@ee.mount-sheikh.edu
abstract: |
  Enter the text of your abstract here.
keywords:
  - blah
  - blee
  - bloo
  - these are optional and can be removed
bibliography: references.bib
output: 
  rticles::arxiv_article:
    number_sections: no
    keep_tex: true
    includes:
      in_header: header.tex
---

@@

getOption("mc.cores", parallel::detectCores())

>>>>

---
title: Main manuscript
authors:
  - name: David S. Hippocampus
    thanks: Use footnote for providing further information about author (webpage, alternative address)---*not* for acknowledging funding agencies. Optional.
    department: Department of Computer Science
    affiliation: Cranberry-Lemon University
    location: Pittsburgh, PA 15213
    email: hippo@cs.cranberry-lemon.edu
  - name: Elias D. Striatum
    department: Department of Electrical Engineering
    affiliation: Mount-Sheikh University
    location: Santa Narimana, Levand
    email: stariate@ee.mount-sheikh.edu
abstract: |
  Enter the text of your abstract here.
keywords:
  - blah
  - blee
  - bloo
  - these are optional and can be removed
bibliography: references.bib
lang: en-GB
output: 
  rticles::arxiv_article:
    number_sections: no
    keep_tex: true
    includes:
      in_header: header.tex
---

@@
